Linking hypothesis and number of response options modulate inferred scalar implicature rate

### 2018-05-16 manuscript.tex
submission version

\begin{enumerate}
\def\labelenumi{(\arabic{enumi})}
\setcounter{enumi}{1}
\tightlist
\item
  She owns a cat.
\end{enumerate}

@@

\emph{Scale:} $\langle$cat and dog, cat$\rangle$

@@

>>>>

\begin{enumerate}
\def\labelenumi{(\arabic{enumi})}
\setcounter{enumi}{2}
\tightlist
\item
  She owns a cat.
\end{enumerate}

@@

\emph{Scale:} $\langle$cat and dog, cat$\rangle$\\
~\\

@@

\section{Author Responsibilities}
All authors contributed to the conception and design of the study. MJ conducted the online survey studies; reported the results and performed the statistical analysis; BW conducted the modeling and wrote the discussion section; JD wrote the theoretical introduction, and contributed to the experimental section and the discussion section and the modeling sections. All authors contributed to manuscript revision, read and approved the submitted version.
